### 2019-04-10 chapters/4-discussion.tex
mention shape feats

>>>>

In addition to texture features, shape descriptors might provide information
useful for Gleason score characterization \citep{Hoeks2011}. However, we decided
to leave them out of this study, focusing on texture features only. Including
shape features would have required considerable amount of additional work, and
would make it more important to treat lesions of different prostate regions
differently.
